### 2023-01-31 manuscript.tex
some citation keys fixed [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/bfaaab005d18e6d1a45e17f5adbda0cf18649697.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/bfaaab005d18e6d1a45e17f5adbda0cf18649697/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4054891245

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/484ae8b4b9e9611eeeb1e0e67f96d5b8bd8b70a4/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/484ae8b4b9e9611eeeb1e0e67f96d5b8bd8b70a4}{stain/2022-fdo-paper@484ae8b}
on January 31, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/bfaaab005d18e6d1a45e17f5adbda0cf18649697/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/bfaaab005d18e6d1a45e17f5adbda0cf18649697}{stain/2022-fdo-paper@bfaaab0}
on January 31, 2023.
